---
title: "Out of sample forecasting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Out of sample forecasting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, }

library(GaRPackg)

library(dplyr)

```

In this vignette we'll look an the out of sample forecasting functions.
The forecasting is performed by rolling window method with expanding window by
default.

We start by defining minimal setup for forecasting

```{r import_process_data}

data("gar_data")

partitions_list = list(
  macro = c("gdp_yoy", "ind_prod_israel_yoy"),
  fin = c("credit_yoy", "house_price_yoy")
)


```


```{r run_forecast}

forecast_df = get_gar_forecast(partitions_list = partitions_list,
                               vars_df = gar_data,
                               target_var_name = "gdp_yoy",
                               horizon_list = c(1,12),
                               quantile_vec = c(0.05,0.25,0.5,0.75,0.95))

```


```{r plot_fan_chart, fig.width=6}

actual_df = gar_data %>% 
  select(date, gdp) %>% 
  mutate(actual_values = gdp/lag(gdp,4) - 1)

plot_fan_chart(forecast_df = forecast_df,
               actual_df = actual_df,
               fan_chart_date = max(actual_df$date))

```


## Internal vs explicit preprocessing

The preprocessing is performed by default by \code{get_gar_forecast} based on partition list variable names suffixes. However in case we want to perform the
preprocessing explicitly (for instance in order to take a look at preprocessed variables) we can do that and then pass the preprocessed data to \code{get_gar_forecast}. Let's demonstrate both ways and make sure that they give the same result

The internal (implicit) preprocessing was already performed in the previous example' the results are stored in \code{result} object. Now, let's perform an explicit preprocessing
and compare the result. Note that we need to set the \code{transform_vars_df} flag in \code{run_GaR_analysis} to \code{FALSE} since we have already transformed the data

```{r preprocess_data}

preprocess_data = preprocess_df(df = gar_data,
                                partitions_list = partitions_list)

explicit_preprocessing_result = get_gar_forecast(
  partitions_list = partitions_list,
  vars_df = preprocess_data,
  target_var_name = "gdp_yoy",
  horizon_list = c(1,12),
  quantile_vec = c(0.05,0.25,0.5,0.75,0.95),
  transform_vars_df = FALSE
)

all.equal(forecast_df, explicit_preprocessing_result)

```

