---
title: "Growth at Risk - The Israeli Case"
institute: "Bank of Israel \\newline Research Department"
author: "Michael Gurkov and Osnat Zohar"
date: "July 15, 2019"
classoption: t
output:
  beamer_presentation:
    keep_tex: true
    includes:
      in_header: "C:\\Users\\micha\\Documents\\GaRPackg\\vignettes\\GaR-PresentationPreamble.tex"
    latex_engine: xelatex
bibliography: "GaR.bib"
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, echo = FALSE, message = FALSE,warning = FALSE, comment = "#>"
)
```


```{r, include=FALSE}


```


```{r setup}

devtools::load_all()

setwd(paste0(
  file.path(Sys.getenv("USERPROFILE"),fsep = "\\"),
  "\\Documents\\GaRPackg\\vignettes"))


```


```{r load_libraries}

library(cowplot)

```



```{r Get_partitions, child="Partition-Specs.Rmd"}

```


```{r import_data, child="GaR-ImportAndProcessData.Rmd"}

```


```{r Analysis}

current_partition = partitions_list$basic

results = run.GaR.analysis(partitions_list = current_partition,
                   vars_df = df,
                   target_var_name = "GDP",
                   horizon_list = parameters_list$horizon_list,
                   quantile_vec = parameters_list$quantile_vec,
                   pca.align.list = list(
                     Dom_FCI = list(
                       var_name = "Spread_CPI_corp",
                       positive_direction = FALSE),
                     Dom_Macro = list(var_name = "GDP"),
                     Global = list(var_name = "rate_euro"),
                     FinCycle = list(var_name = "Credit")))


results$reg_df = results$reg_df %>%
  rename_all(~str_remove_all(.,pattern = "_xreg"))

```


# Motivation

\begin {itemize}
\itemsep3em
	\item
	Assessing risks to future economic activity is essential for making knowledgeable forecasts.
	\item
	An important factor: financial vulnerabilities.
	\item
	We provide a methodological tool for assessing risks to growth in Israel using real and financial variables:

	\vspace{1em}

	\begin{center}
		~
	\begin{beamerboxesrounded}[width=0.75\linewidth]{}
		Given current macro-financial conditions, what is the distribution of
		expected economic growth?
	\end{beamerboxesrounded}
	~
	\end{center}

\end{itemize}









# Motivation

\centering
Quantile Regressions of YoY GDP Growth Four Quarters Ahead

\vspace{3mm}

```{r plot_gdp_credit}

temp_df = df %>%
  select(all_of(c("GDP","Credit"))) %>%
  add_leads_to_target_var(target_var_name = "GDP",
                          leads_vector = 4) %>%
  filter(complete.cases(.))

plot_list = map(list("GDP","Credit"), function(temp_var){
 
temp_qreq = rq(paste0("GDP_4","~",temp_var),
               tau = c(0.05,0.5,0.95),
               data = temp_df) %>%
  coefficients() %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column() %>%
  mutate(rowname = str_remove_all(rowname, "tau= ")) %>% 
  rename(Quantile = rowname,
         my_int = `(Intercept)`,
         my_slope = !!sym(temp_var))

temp_plot = temp_df %>%
  ggplot(aes(x = !!sym(temp_var),
             y = GDP_4)) +
  geom_point() +
  geom_abline(data = temp_qreq,
              aes(intercept = my_int,
                  slope = my_slope,
                  color = Quantile)) +
  scale_x_continuous(
    labels = scales::percent_format(accuracy = 1)) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)) +
  xlab(paste("YoY", temp_var, "growth")) +
  ylab((paste("YoY GDP growth 4 quarters ahead"))) +
  ggtitle(temp_var) + 
  theme_bw() + 
  theme(legend.position = "none")

  return(temp_plot)
  
})

legend_p = get_legend(
  plot_list[[1]] + theme(legend.position = "bottom"))

plot_grid(plot_grid(plotlist = plot_list,ncol = 2),
          nrow = 2,
          legend_p, rel_heights = c(1,0.2))

```





# Main Results

\begin{itemize}
\item
In-sample properties of the predictive distribution:
  \begin{enumerate}
	\item
	\textbf{Symmetric} -- upside and downside risks are balanced. 
	\item
	\textbf{Forecast uncertainty} rises when the median forecast decreases. 
	\item			
	\textbf{``Volatility paradox''} -- an increase in credit or asset prices is correlated with short-term GDP growth, but contributes to long-term downside risks. 
  \end{enumerate}
\item
These properties are robust to variable selection.
\item
Out-of-sample forecast performance is impaired.
\item
Insights may help construct a better forecasting model  (future research).  
\end{itemize}
		

