
```{r load_prediction_libraries}

library(stargazer)

```


```{r set_forecast_parameters}

forecast_parameters = list(win_len = 30, out_of_sample_step = 1)

forecast_comparisons = list()

```


\subsection{Forecast accuracy}

We use in sample and out of sample comparison in order to test the robustness of partition
specification. The out of sample forecast is constructed by estimation of a rolling window of length `r forecast_parameters$win_len` and forecasting `r forecast_parameters$out_of_sample_step` step ahead.

\subsection{Comparison to actual GDP}

We take actual GDP YoY growth rates and compare them with the predicted median YoY GDP growth rates. The matching between the actual and forecasted values is based on
forecasted period


```{r make_actual_gdp_df}

actual_gdp_df = df %>% 
  select(Date, GDP) %>% 
  filter(complete.cases(.)) %>% 
  rename(GDP_actual = GDP) %>% 
  mutate(Forecast_Period = paste(Date - 1, Date, sep = "-")) %>% 
  select(-Date)

```


```{r GaR_forecast}

gar_forecast_df = lapply(c("fixed","expanding"),
                         function(temp_win_type){
  
  temp_res = get.gar.forecast(
    gar_obj = results,
    win_len = forecast_parameters$win_len,
    quantile_vec = parameters_list$quantile_vec,
    out_of_sample_step = forecast_parameters$out_of_sample_step,
    win_type = temp_win_type) %>% 
    filter(complete.cases(.)) %>% 
    mutate(Win_Type = temp_win_type)
  
  return(temp_res)
}) %>% 
  bind_rows() %>% 
  mutate(Date = as.yearqtr(Date)) %>% 
  mutate(Forecast_Period = paste(Date + as.numeric(Horizon) * 0.25 - 1,
                                  Date + as.numeric(Horizon) * 0.25,
                                  sep = "-"))



```


```{r gar_actual_comparison}

forecast_comparisons$gar_actual = gar_forecast_df %>% 
  filter(Quantile == "0.50") %>% 
  select(-Quantile) %>% 
  inner_join(.,actual_gdp_df, by = "Forecast_Period") %>% 
  mutate(Error = GDP_actual - GaR_forecast)



```


```{r plot_gar_actual_rmse}

ggplot(forecast_comparisons$gar_actual %>% 
         group_by(Horizon,Forecast_Status,Win_Type) %>% 
         summarise(RMSE = sqrt(mean(Error ^ 2)), .groups = "drop"),
       aes(x = reorder(Horizon, as.numeric(Horizon)), y = RMSE, fill = Horizon)) + 
  facet_grid(rows = vars(Forecast_Status), cols = vars(Win_Type), scales = "free_y") + 
  geom_col(width = 0.5) + 
  labs(x = "", y = "", title = "Forecast fit") + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) + 
  theme_bw() + 
  theme(legend.position = "bottom")

```


```{r plot_actual_quantile_fit_score}

forecast_periods = unique(gar_forecast_df$Forecast_Period)[
  unique(gar_forecast_df$Forecast_Period) %in% actual_gdp_df$Forecast_Period]


forecast_comparisons$gar_actual_fit_score = lapply(forecast_periods,
                                                   function(temp_period){
  
  actual_gdp = actual_gdp_df$GDP_actual[actual_gdp_df$Forecast_Period == temp_period]
  
  temp_df = gar_forecast_df %>%
    filter(Forecast_Period == temp_period) %>% 
    group_by(Horizon, Win_Type,Forecast_Status) %>% 
    summarise(Score = quantile.fit.score(realized_estimate = actual_gdp,
                               quantile_values = GaR_forecast,
                               quantiles = as.numeric(Quantile)),
              .groups = "drop") %>% 
    ungroup() %>% 
    mutate(Forecast_Period = temp_period)
  
  return(temp_df)
  
  
  
}) %>% 
  bind_rows() %>% 
  mutate(Horizon = factor(Horizon, leves = c("1","8","12")))


ggplot(forecast_comparisons$gar_actual_fit_score %>% 
  group_by(Horizon,Win_Type,Forecast_Status) %>% 
  summarise(SD = sd(Score), .groups = "drop"),
  aes(x = Horizon, y = SD, fill = Horizon)) + 
  facet_grid(rows = vars(Forecast_Status), cols = vars(Win_Type), scales = "free_y") + 
  geom_col(width = 0.5) + 
  labs(x = "", y = "", title = "Forecast fit - quantile fit score") + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) + 
  theme_bw() + 
  theme(legend.position = "bottom")


```



\section{Comparison to staff forecast}

```{r, make_staff_forecast}

staff_forecast_df_h1 = raw_df %>% 
  select(Date, staff_1Q) %>% 
  rename_all(.funs = list(~str_remove(.,"staff_"))) %>% 
  gather(key = Quarter,value = Forecast, - Date) %>% 
  filter(complete.cases(.)) %>% 
  left_join(.,raw_df %>% 
              select(Date, GDP) %>% 
              mutate(GDP = GDP / lag(GDP,3) - 1)) %>% 
  mutate(Staff_Forecast = Forecast * 0.25 * 0.01 + GDP) %>% 
  select(Date,Staff_Forecast) %>% 
  mutate(Forecast_Period = paste(Date - 0.75,Date + 0.25, sep = "-")) %>% 
  mutate(Horizon = "1")

staff_forecast_df_h8 = raw_df %>% 
  select(Date, staff_5Q, staff_6Q, staff_7Q, staff_8Q) %>% 
  rename_all(.funs = list(~str_remove(.,"staff_"))) %>% 
  gather(key = Quarter,value = Forecast, - Date) %>% 
  group_by(Date) %>% 
  summarise(Staff_Forecast = mean(Forecast) * 0.01) %>% 
  ungroup() %>% 
  filter(complete.cases(.)) %>% 
  mutate(Forecast_Period = paste((Date + 1),(Date + 2), sep = "-")) %>% 
  mutate(Horizon = "8")

staff_forecast = bind_rows(staff_forecast_df_h1,
                           staff_forecast_df_h8) %>% 
  mutate(Date = as.yearqtr(Date)) %>% 
  inner_join(.,actual_gdp_df, by = "Forecast_Period") %>% 
  mutate(Error_staff = GDP_actual - Staff_Forecast)

rm(staff_forecast_df_h8, staff_forecast_df_h1)



```


```{r make_comparison_between_staff_and_gar_forecast}

forecast_comparisons$gar_staff = forecast_comparisons$gar_actual %>% 
  rename(Error_gar = Error) %>% 
  inner_join(., staff_forecast %>% 
              select(-GDP_actual),
            by = c("Date","Horizon", "Forecast_Period"))

```


```{r plot, eval=FALSE}

ggplot(forecast_comparisons$gar_staff %>% 
         filter(Forecast_Status == "Out of Sample") %>% 
         select(Date,Horizon,Win_Type,Error_gar,Error_staff) %>% 
         gather(key = Method, value = Error, -Date,-Horizon,-Win_Type),
       aes(x = Date, y = Error, color = Method)) + 
  geom_point() + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "blue") + 
  labs(x = "", y = "", title = "Forecast difference \n (GaR - Staff)") + 
  facet_grid(rows = vars(Horizon),cols = vars(Win_Type),scales = "free") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom")

```


```{r compare_forecast}

rmse_df = gar_staff_comparison_df %>% 
  filter(Forecast_Status == "Out of Sample") %>% 
  select(Date,Horizon,Win_Type,Error_gar,Error_staff) %>% 
  gather(key = Method, value = Error, -Date,-Horizon,-Win_Type) %>%
  group_by(Win_Type, Horizon, Method) %>% 
  summarise(RMSE = sqrt(mean(Error ^ 2))) %>% 
  ungroup()

ggplot(rmse_df, aes(x = Method, y = RMSE  * 100, fill = Method)) + 
  geom_col(position = "dodge", width = 0.4) + 
  facet_grid(rows = vars(Horizon),cols = vars(Win_Type),scales = "free") + 
  labs(x = "", y = "RMSE(%)", title = "GaR vs Staff forecast fit") +
  theme_bw() + 
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))




```


\section{Comparison to domestic macro}

```{r macro_comparison}

macro_gar = run.GaR.analysis(partitions_list = partitions_list$macro,
                                vars_df = df,
                                horizon_list = parameters_list$horizon_list,
                                quantile_vec = parameters_list$quantile_vec,
                                run_ols_reg = FALSE)

macro_gar_forecast_df = lapply(c("fixed","expanding"),
                         function(temp_win_type){
  
  temp_res = get.gar.forecast(
    gar_obj = macro_gar,
    win_len = forecast_parameters$win_len,
    quantile_vec = parameters_list$quantile_vec,
    out_of_sample_step = forecast_parameters$out_of_sample_step,
    win_type = temp_win_type) %>% 
    filter(complete.cases(.)) %>% 
    mutate(Win_Type = temp_win_type)
  
  return(temp_res)
}) %>% 
  bind_rows() %>% 
  mutate(Date = as.yearqtr(Date))


gar_macro_comparison_df = list(gar_forecast_df %>% 
                                 filter(Quantile == "0.50") %>% 
                                 select(-Quantile),
                               macro_gar_forecast_df %>% 
                                 filter(Quantile == "0.50") %>% 
                                 select(-Quantile)) %>% 
  reduce(inner_join, by = c("Date","Horizon","Forecast_Status","Win_Type"),
         suffix = c("_full", "_macro"))  %>% 
  mutate(Forecast_Period = paste(Date + as.numeric(Horizon) * 0.25 - 1,
                                  Date + as.numeric(Horizon) * 0.25,
                                  sep = "-"))  %>% 
  inner_join(.,actual_gdp_df, by = "Forecast_Period") %>% 
  mutate_at(.vars = vars(starts_with("GaR_forecast")),
            .funs = list(Error = ~ . - GDP_actual))

```


```{r plot_macro_rmse}

gar_macro_comparison_rmse = gar_macro_comparison_df %>% 
  group_by(Horizon, Forecast_Status,Win_Type) %>% 
  summarise_at(.vars = vars(ends_with("Error")),
               .funs = list(~ sqrt(mean(. ^ 2)) * 100)) %>% 
  ungroup() %>% 
  pivot_longer(cols = ends_with("Error"),names_to = "Category",
               values_to = "RMSE")

ggplot(gar_macro_comparison_rmse %>% 
         filter(Forecast_Status == "Out of Sample"),
       aes(x = Category ,y = RMSE, fill = Category)) + 
  geom_col(position = "dodge", width = 0.5) + 
  facet_grid(rows = vars(Horizon), cols = vars(Win_Type)) +
  theme_bw() + 
  theme(legend.position = "bottom")



```


\section{Residuals analysis}
