
```{r get_quantiles_df}


dist_quantile_df = calculate_skew_and_iqr(results)

factor_quantiles_df = extract_factor_contribution_from_gar_model(results)


```



\subsection{Median - Variance correlation}


```{r median_variance_scatter_plot}

ggplot(dist_quantile_df %>% 
         select(horizon, iqr, q0.05), aes(x = iqr, y = q0.05)) + 
  geom_point() + 
  stat_smooth(method = "lm") + 
  facet_wrap(~horizon) + 
  labs(x = "Variance", y = "Median", title = "Median vs Variance") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5))
    

```


```{r plot_median_variance_corr}

dist_quantile_df %>% 
  select(date,horizon, iqr, q0.50) %>%
  group_by(horizon) %>% 
  summarise(corr = cor(iqr,q0.50)) %>% 
  ggplot(aes(x = horizon, y = corr)) + 
  geom_col(width = 0.5) + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "blue") + 
  theme_bw()

```

subsection{Risk Asymmetry}
The "risk asymmetry" phenomenon refers to the fact that the left tail of the forecasted growth distribution (the depressed growth scenarios) is quite volatile relative to the right
tail of the distribution meaning that the downside growth risk is much more
severe than upside risk. The empirical representation of this phenomenon is that a distance between
of the 5th percentile from the median should be larger relative to the distance of the 95th 
percentile from the median.


```{r plot_risk_assymetry, fig.height=8}

ggplot(dist_quantile_df, aes(x = date, y = skew)) + 
  geom_line() + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "blue") + 
  labs(x = "", y = "", title = "Risk asymmetry") + 
  facet_wrap(~horizon, scales = "free", ncol = 1) + 
  theme_bw() + 
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))

```


