
```{r get_quantiles_df}

dist_quantile_df = results$gar_fitted_df %>% 
  pivot_wider(names_from = Quantile, values_from = GaR_fitted) %>% 
  rename_at(.vars = vars(grep("\\d",names(.),value = TRUE)),
            .funs = list(~paste0("Q_",.))) %>% 
  group_by(Horizon) %>% 
  mutate(Skew = (0.5 * Q_0.75 + 0.5 * Q_0.25 - Q_0.5) /
           (0.5 * Q_0.75 - 0.5 * Q_0.25)) %>% 
  mutate(IQR = Q_0.75 - Q_0.25) %>% 
  ungroup() %>% 
  mutate(Horizon = forcats::as_factor(Horizon))


factor_quantiles_df = lapply(names(results$qreg_result),
                             function(temp_name){
  
  temp_df = results$qreg_result[[temp_name]]$coefficients

  temp_df = temp_df %>% 
  as.data.frame() %>% 
  rename_at(.vars = vars(grep("tau",names(.),value = TRUE)),
            .funs = list(~str_replace(.,"tau= ","Q_"))) %>% 
  mutate(Factor = rownames(.)) %>% 
  mutate(IQR = Q_0.95 - Q_0.05) %>% 
  mutate(Horizon = temp_name)

  return(temp_df)
  
}) %>% 
  bind_rows() %>% 
  mutate(Horizon = factor(Horizon, unique(Horizon))) %>% 
  filter(!Factor == "(Intercept)")


iqr_horizon_corr_mat = dist_quantile_df %>% 
  select(date,Horizon, IQR) %>% 
  spread(key = Horizon,value = IQR) %>% 
  select(-date) %>% 
  cor(use = "pairwise.complete.obs")


median_iqr_corr_mat = dist_quantile_df %>% 
  select(date,Horizon, IQR, Q_0.5) %>%
  group_by(Horizon) %>% 
  summarise(Corr = cor(IQR,Q_0.5))
  


```




\subsection{Median - Variance correlation}


```{r median_variance_scatter_plot}

ggplot(dist_quantile_df %>% 
         select(Horizon, IQR, Q_0.5), aes(x = IQR, y = Q_0.5)) + 
  geom_point() + 
  stat_smooth(method = "lm") + 
  facet_wrap(~Horizon) + 
  labs(x = "Variance", y = "Median", title = "Median vs Variance") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5))
    

```


```{r plot_median_variance_corr}

ggplot(median_iqr_corr_mat, aes(x = Horizon, y = Corr)) + 
  geom_col(width = 0.5) + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "blue") + 
  theme_bw()

```



\subsection{Volatility Paradox}
The volatility paradox describes a phenomenon where stable conditions today allow risk accumulation
that realize in the future. The empirical representation of this phenomenon is a negative
correlation between IQR (Inter Quartile Range) in the short and long term

```{r output_VP_corr_mat, results='asis'}

print(xtable(iqr_horizon_corr_mat), comment = FALSE)
  
```

We can also try to asses the contribution of each factor to the volatility paradox. A factor will decrease the distribution volatility if the effect of
The volatility paradox suggest that the 

```{r factors_IQR}

ggplot(factor_quantiles_df, aes(x = Horizon, y = IQR, group = 1)) + 
  geom_path() + 
  geom_point() + 
  labs(y = "") + 
  facet_wrap(~Factor) + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5))

```

\subsection{Risk Asymmetry}
The "risk asymmetry" phenomenon refers to the fact that the left tail of the forecasted growth distribution (the depressed growth scenarios) is quite volatile relative to the right
tail of the distribution meaning that the downside growth risk is much more
severe than upside risk. The empirical representation of this phenomenon is that a distance between
of the 5th percentile from the median should be larger relative to the distance of the 95th 
percentile from the median.


```{r plot_risk_assymetry, fig.height=8}

ggplot(dist_quantile_df, aes(x = date, y = Skew)) + 
  geom_line() + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "blue") + 
  labs(x = "", y = "", title = "Risk asymmetry") + 
  facet_wrap(~Horizon, scales = "free", ncol = 1) + 
  theme_bw() + 
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))

```



```{r plot_mean_median_diff, fig.height=8, eval=FALSE}


ggplot(dist_quantile_df, aes(x = date, y = OLS - Q_0.5)) + 
  geom_line() + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "blue") + 
  labs(x = "", y = "",
       title = "Difference between mean (OLS) and median (quantile) regressions ") + 
  facet_wrap(~Horizon, scales = "free", ncol = 1) + 
  theme_bw() + 
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))

```

