---
title: "Growth at Risk - The Israeli Case"
institute: "Bank of Israel \\newline Research Department"
author: "Michael Gurkov and Osnat Zohar"
date: "July 15, 2019"
classoption: t
output:
  beamer_presentation:
    includes:
      in_header: "C:\\Users\\internet\\Documents\\GaRPackg\\vignettes\\GaR-PresentationPreamble.tex"
    latex_engine: xelatex
bibliography: "GaR.bib"
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, echo = FALSE, message = FALSE,warning = FALSE, comment = "#>"
)
```


```{r, include=FALSE}


```


```{r setup}

devtools::load_all()

setwd(paste0(
  file.path(Sys.getenv("USERPROFILE"),fsep = "\\"),
  "\\Documents\\GaRPackg\\vignettes"))


```


```{r load_libraries}

library(cowplot)

```



```{r Get_partitions, child="Partition-Specs.Rmd"}

```


```{r import_data, child="GaR-ImportAndProcessData.Rmd"}

```


```{r Analysis}

current_partition = partitions_list$basic

results = run.GaR.analysis(partitions_list = current_partition,
                   vars_df = df,
                   target_var_name = "GDP",
                   horizon_list = parameters_list$horizon_list,
                   quantile_vec = parameters_list$quantile_vec,
                   pca.align.list = list(
                     Dom_FCI = list(
                       var_name = "Spread_CPI_corp",
                       positive_direction = FALSE),
                     Dom_Macro = list(var_name = "GDP"),
                     Global = list(var_name = "rate_euro"),
                     FinCycle = list(var_name = "Credit")))


results$reg_df = results$reg_df %>%
  rename_all(~str_remove_all(.,pattern = "_xreg"))

```


```{r set_params}

pca_list = results$pca

pca_variance = lapply(names(pca_list), function(temp_name){

  data.frame(Name = temp_name,
             Variance = round(pca_list[[temp_name]]$pca$sdev[1] ^ 2 /
                                sum(pca_list[[temp_name]]$pca$sdev ^ 2),3),
             stringsAsFactors = FALSE)



}) %>%
  bind_rows()

plot_names_list = list("Macro","Global","Fin. Conditions",
                       "Fin. Cycle")

names(plot_names_list) = names(pca_list)

coeff_df = lapply(names(results$qreg_result),
                  function(temp_name){
  
  temp_coeff_df = results$qreg_result[[temp_name]]$coefficients %>% 
    as.data.frame() %>% 
    rename_all(.funs = list(~str_remove_all(.,"tau= "))) %>% 
    mutate(Partition = rownames(.)) %>% 
    gather(key = Quantile,value = Coeff, - Partition) %>% 
    mutate(Horizon = temp_name)
    
  
  return(temp_coeff_df)

}) %>% 
  bind_rows() %>% 
  mutate(Horizon = factor(Horizon, levels = c(1,8,12))) %>% 
  filter(!Partition == "(Intercept)") %>% 
  mutate(Partition = str_remove_all(Partition,"_xreg"))
  
my_lab = function(string){
  
  paste0("h = ", string)
  
}

```



```{r calculate_gar_contribution}

factors_df = map_dfr(names(results$qreg_result),function(temp_name){
    
    data_mat = results$reg_df %>%
      select(names(current_partition)) %>%
      as.matrix()
    
    coef_vec = coefficients(results$qreg_result[[temp_name]])[-1,1]
    
    gar_factors_df =  t(t(data_mat) * coef_vec)
    
    gar_factors_df = cbind(Date = results$reg_df$Date,
                           as.data.frame(gar_factors_df)) %>% 
      mutate(Horizon = temp_name)
    
    return(gar_factors_df)
 
                        })

factors_df = factors_df %>% 
  rename(Macro = Dom_Macro) %>% 
  rename(`Fin. Cycle` = FinCycle) %>% 
  rename(`Fin. Conditions` = Dom_FCI) %>% 
  pivot_longer(cols = -c(Date,Horizon), names_to = "partition")
  




```


# Motivation

\begin {itemize}
\itemsep3em
	\item
	Assessing risks to future economic activity is essential for making knowledgeable forecasts.
	\item
	An important factor: financial vulnerabilities.
	\item
	We provide a methodological tool for assessing risks to growth in Israel using real and financial variables:

	\vspace{1em}

	\begin{center}
		~
	\begin{beamerboxesrounded}[width=0.75\linewidth]{}
		Given current macro-financial conditions, what is the distribution of
		expected economic growth?
	\end{beamerboxesrounded}
	~
	\end{center}

\end{itemize}











# Motivation

\centering
Quantile Regressions of YoY GDP Growth Four Quarters Ahead

\vspace{3mm}

```{r plot_gdp_credit, cache=TRUE}

temp_df = df %>%
  select(all_of(c("GDP","Credit"))) %>%
  add_leads_to_target_var(target_var_name = "GDP",
                          leads_vector = 4) %>%
  filter(complete.cases(.))

plot_list = map(list("GDP","Credit"), function(temp_var){
 
temp_qreq = rq(paste0("GDP_4","~",temp_var),
               tau = c(0.05,0.5,0.95),
               data = temp_df) %>%
  coefficients() %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column() %>%
  mutate(rowname = str_remove_all(rowname, "tau= ")) %>% 
  rename(Quantile = rowname,
         my_int = `(Intercept)`,
         my_slope = !!sym(temp_var))

temp_plot = temp_df %>%
  ggplot(aes(x = !!sym(temp_var),
             y = GDP_4)) +
  geom_point() +
  geom_abline(data = temp_qreq,
              aes(intercept = my_int,
                  slope = my_slope,
                  color = Quantile)) +
  scale_x_continuous(
    labels = scales::percent_format(accuracy = 1)) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1)) +
  xlab(paste("YoY", temp_var, "growth")) +
  ylab((paste("YoY GDP growth 4 quarters ahead"))) +
  ggtitle(temp_var) + 
  theme_bw() + 
  theme(legend.position = "none")

  return(temp_plot)
  
})

legend_p = get_legend(
  plot_list[[1]] + theme(legend.position = "bottom"))

plot_grid(plot_grid(plotlist = plot_list,ncol = 2),
          nrow = 2,
          legend_p, rel_heights = c(1,0.2))

```


<!-- # The Growth at Risk (GaR) approach -->

<!-- - Proposed by @Adrian2019, operationalized by the IMF [@Prasad2019]. -->
<!-- - Applied to: -->
<!--   - Italy [@Alessandri2019] -->
<!--   - UK [@Aikman2018] -->
<!--   - Advanced economies [@Aikman2018] -->
<!--   - Developed econimies [@Komatsuzaki2019, @Bespalova2019] -->

<!-- - GaR is a linear model of density forecast -->
<!--   - based on quantile regression -->
<!--   - Parsimonious -->
<!--   - Easy to interpret -->

<!-- - Possible uses: -->
<!--   1. Regular assessment of risk (e.g tracking 5th percentile of forecast) -->
<!--   2. Provide empirical evidence to support macro-financial modeling efforts  -->
<!--   (joint projects IMF) -->








# Main Results

\begin{itemize}
\item
In-sample properties of the predictive distribution:
  \begin{enumerate}
	\item
	\textbf{Symmetric} -- upside and downside risks are balanced. 
	\item
	\textbf{Forecast uncertainty} rises when the median forecast decreases. 
	\item			
	\textbf{``Volatility paradox''} -- an increase in credit or asset prices is correlated with short-term GDP growth, but contributes to long-term downside risks. 
  \end{enumerate}
\item
These properties are robust to variable selection.
\item
Out-of-sample forecast performance is impaired.
\item
Insights may help construct a better forecasting model  (future research).  
\end{itemize}
		





# Outline


# Methodology
\begin{enumerate}
	\item
	\textbf{Partition data:} divide a large number of variables into $K$ groups ($K$ small).
	
	\item
	\textbf{Dimension reduction} to alleviate overfitting:
	\begin{itemize}
		\item
		From each group $k\in\{1,...,K\}$, generate a single regressor $x^k_t$ 
		\item
		Method: first principal component
	\end{itemize}
	
	\item
	\textbf{Quantile regressions --}
	estimate a forecast equation for each quantile $\tau$ and horizon $h$:
	$$
	Q^{\tau}_{t,h}=\beta^{\tau}_hX_t+\epsilon^{\tau}_{t,h}
	$$
	where $ X_t=[1, x^1_t, ... , x^K_t]$
	\begin{flushright}
		\hyperlink{quantile reg}{\beamerbutton{quantile reg}}
	\end{flushright}
\end{enumerate}


# Data Partitioning{Sample: 1996Q3-2019Q4}

\scriptsize
\begin{tabularx}{\linewidth}{X |X |X | X}
	Macro 						& Global & Fin.  Conditions & Fin. Cycle\\
	\hline 
	& & & \\
	GDP 						& GDP - US, Euro 			& BoI rate 				& credit\\ 
	& & & \\
	State-of-the-Economy index 	& OECD imports				& TA35 implied vol. 	& house prices \\
	& & & \\
	unemployment gap 			& monetary rate - US, Euro  & ILS-USD implied vol. 	& TA125  \\
	& & & \\
								& S\&P500					& corp. bond spreads &  \\
	& & & \\							
								& eurostoxx600				& term-spread 			& \\
	& & & \\
								&  non-energy commodity prices			& US-Israel gov. bond spread &\\
	& & & \\
								& Brent oil price &  & \\
	& & & \\
								& US term spread			&						& \\
	& & & \\	
								& VIX						& 						& \\
\end{tabularx}

\flushright
\vspace{-10mm}
\hyperlink{PCA_loadings}{\beamergotobutton{PCA loadings}}

\hyperlink{PCA}{\beamergotobutton{PCA time-sereis}}




# $1^{st}$ Principal Components

```{r plot_pca_timeseries}

pca_timeseries_plots = lapply(names(pca_list), function(name){
  
  ggplot(data.frame(x = pca_list[[name]]$time_index,
                  y = pca_list[[name]]$pca_obj$x[,1]),
         aes(x = x, y = y)) + 
    geom_line() + 
    labs(title = plot_names_list[name], x = "", y = "") + 
    scale_x_yearqtr() +
    theme_bw()

  })

plot_grid(plotlist = pca_timeseries_plots, nrow = 2)

```


\flushleft
\vspace{-10mm}
\hyperlink{MoreCoefs}{\beamergotobutton{more coefs}}


# Quantile regression coefficients

```{r dom_macro_plot}

ggplot(coeff_df %>% 
         filter(Partition == "Dom_Macro") %>% 
         filter(Horizon %in% c(1,12)),
         aes(x = Quantile, y= Coeff)) + 
  geom_col(width = 0.5) + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "blue") + 
  labs(x = "Quantile", y = "",
       title = "Macro coefficients") + 
  facet_wrap(~ Horizon, labeller = labeller(Horizon = my_lab)) + 
  theme_bw()



```



# Quantile regression coefficients

```{r fin_cycle_plot}

ggplot(coeff_df %>% 
         filter(Partition == "FinCycle") %>% 
         filter(Horizon %in% c(1,12)),
         aes(x = Quantile, y= Coeff)) + 
  geom_col(width = 0.5) + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "blue") + 
  labs(x = "Quantile", y = "",
       title = "Fin.Cycle coefficients") + 
  facet_wrap(~ Horizon,labeller = labeller(Horizon = my_lab)) + 
  theme_bw()

```


```{r pca_loadings, eval=FALSE}

pca_plots = lapply(names(pca_list), function(name){
  
  pca_var = round(pca_variance$Variance
                  [pca_variance$Name == name] * 100,0)
  
  bar_plot = ggplot(data.frame(Name = names(pca_list[[name]]$pca$rotation[,1]),
                  Val = pca_list[[name]]$pca$rotation[,1]),
       aes(x = reorder(Name, Val), y = Val)) +
  geom_bar(stat = "identity", width = 0.5) +
  labs(x = "", y = "", title = paste0(
    plot_names_list[[name]], " (" ,pca_var, "%)")) +
  coord_flip() +
  theme_bw()
  
  rm(pca_var)
  
  return(bar_plot)
  

})

plot_grid(plotlist = pca_plots)


```


# Volatility Paradox

\begin{itemize}
	\item
	Financial cycle factor is correlated with growth in the short term, but also with
	elevated risks in the long term. 
	\item
	Consistent with: 
	\vspace{2mm}
	\begin{centering}
		~	
		\begin{beamerboxesrounded}[width=0.9\linewidth]{Volatility Paradox  \scriptsize \citep{brunnermeier2014macroeconomic}}
			Low risks (which contribute to short-term growth), encourage the accumulation of risks in the medium to long term. 
		\end{beamerboxesrounded}		
	\end{centering}
	\item
	Mechanisms:
\end{itemize}



# Short-Term Forecast of 5th Percentile More Volatile Than Long-Term Forecast
Forecast of 5th Percentile, 1Q and 12Q Ahead

```{r plot_events_plot}

recessions = read.csv(paste0(
  file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
  "\\OneDrive - Bank Of Israel\\",
  "Data\\BoI\\GaR_Data","\\recessions.csv")) %>% 
  mutate(across(c(Start, End), ~as.yearqtr(.)))

events = read.csv(paste0(
  file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
  "\\OneDrive - Bank Of Israel\\",
  "Data\\BoI\\GaR_Data","\\events.csv")) %>% 
  mutate(across(c(Start, End), ~as.yearqtr(.)))

predict_df =  data.frame(
  Date = results$reg_df$Date,
  Horizon_1 = predict(results$qreg_result$`1`,
                newdata = results$reg_df %>% 
                  rename_at(vars(-Date, -starts_with("GDP")),
                            ~paste0(.,"_xreg")))[,1],
  Horizon_12 = predict(results$qreg_result$`12`,
                newdata = results$reg_df %>% 
                  rename_at(vars(-Date, -starts_with("GDP")),
                            ~paste0(.,"_xreg")))[,1]) %>% 
  pivot_longer(cols = -Date,
               names_to = "Horizon",
               values_to = "GaR")


ggplot() + 
  ylim(c(-0.12,0.08)) + 
  geom_point(data = predict_df,
             mapping = aes(x = Date, y = GaR, color = Horizon)) + 
  geom_line(data = predict_df,
            mapping = aes(x = Date, y = GaR, color = Horizon)) + 
  geom_rect(data = recessions,
            mapping = aes(xmin = Start, xmax = End,
                          ymin = -Inf, ymax = Inf),
            fill = "lightblue", alpha = 0.5) +
  theme_bw() + 
  ylab(NULL) + xlab(NULL)
  ggtitle("Forecast of 5th Percentile, 1Q and 12Q Ahead") + 
  geom_point(data = predict_df %>% 
             filter(Date %in% events$Start),
           mapping = aes(x = Date, y = GaR),
           color = "blue") + 
  geom_segment(data = predict_df %>% 
                 filter(Date %in% events$Start) %>% 
                 slice(1:2),
             mapping = aes(x = Date, y = c(0.0745,0.0745),
                           xend = Date, yend = GaR),
             arrow = arrow(length = unit(0.1,"cm")),
             color = "blue") + 
  geom_text(data = events,
            mapping = aes(x = Start + 1, y = c(0.08,0.08,0.06),
                                          label = Event),
            color = "blue") + 
  theme(legend.position = "bottom", legend.title = element_blank())


```



# The Global factor contributes to risk idtinification in the short term, Financial Cycle -- in the long term

```{r plot_factor_decomposition}

factors_df %>% 
  filter(Horizon %in% c(1,12)) %>% 
  ggplot() + 
  geom_col(mapping = aes(x = Date, y = value,
                                         fill = partition),
           position = "stack", size = 5) +
  geom_line(data = . %>%
              group_by(Date,Horizon) %>%
              summarise(Total = sum(value),.groups = "drop") %>%
              ungroup(),mapping =  aes(x = Date, y = Total), size = 1) +
  facet_wrap(~Horizon,labeller = labeller(Horizon = my_lab)) + 
  xlab(NULL) + ylab(NULL) + 
  ggtitle("Contribution of Factors to the Forecast of the 5th Percentile") + 
  scale_fill_viridis_d(option = "plasma") +
  theme_bw() + 
  theme(legend.position = "bottom",
        legend.title = element_blank())


```

# Forecast Median and Dispersion are Negatively Correlated

```{r plot_median_dispersion}

results$gar_fitted_df %>% 
  mutate(Horizon = factor(Horizon, levels = c(1,4,8,12))) %>% 
  pivot_wider(id_cols = c(Date,Horizon),
              names_from = "Quantile",
              values_from = "GaR_fitted") %>% 
  mutate(IQR = `0.75` - `0.25`) %>% 
  ggplot(aes(x = IQR, y = `0.5`)) + 
  geom_point() + 
  stat_smooth(method = "lm") + 
  facet_wrap(~Horizon, scales = "free") + 
  labs(x = "Dispersion", y = "Median", title = "Dispersion vs Variance") +
  theme_bw()



```

