
<<<<<<< HEAD
```{r plot_quantreq_rho, fig.height=8, eval=FALSE}

rho_data = lapply(results$quantile_reg, function(temp_qreg){temp_qreg$rho}) %>% 
  bind_rows() %>% 
  mutate(Quantile = as.character(quantile_vec)) %>% 
  gather(key = Horizon,value = Rho, -Quantile)

ggplot(data = rho_data, aes(x = Quantile, y = Rho)) + 
  geom_bar(stat = "identity") + 
  labs(title = "Distribution of rho by quantiles and horizon") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  facet_wrap(~Horizon)

```

=======
>>>>>>> temp

```{r plot_quant_reg_long_series_1}

<<<<<<< HEAD
plot.qreg.coeffs(results$quantile_reg[1])
=======
plot.qreg.coeffs(results$qreg_result[1])
>>>>>>> temp

```



```{r plot_quant_reg_long_series_2}

<<<<<<< HEAD
plot.qreg.coeffs(results$quantile_reg[2])
=======
plot.qreg.coeffs(results$qreg_result[2])
>>>>>>> temp

```



```{r plot_quant_reg_long_series_3}

<<<<<<< HEAD
plot.qreg.coeffs(results$quantile_reg[3])
=======
plot.qreg.coeffs(results$qreg_result[3])
>>>>>>> temp

```


