
```{r load_prediction_libraries}

library(stargazer)

```


```{r GaR_forecast}

gar_forecast = get.gar.forecast(gar_obj = results[[1]],
                        win_len = 30,
                        quantile_vec = parameters_list$quantile_vec,
                        out_of_sample_step = 1)

```


```{r actual_values}

gar_actual_df = results[[1]]$reg_df %>% 
  select(Date, starts_with("GDP_growth")) %>% 
  rename_at(.vars = vars(starts_with("GDP_growth")),
            .funs = list(~str_replace(string = .,pattern = "GDP_growth_",
                                     replacement = ""))) %>% 
  gather(key = Horizon,value = GaR_actual,-Date)

```


```{r naive_forecast}

naive_forecast_df = results[[1]]$reg_df %>% 
  select(Date,GDP_F) %>% 
  mutate(Naive_Next_Q = c(rep(NA,3),rollmean(GDP_F,4))) %>% 
  mutate(Naive_Next_Q = lag(Naive_Next_Q))

```


```{r staff_forecast}

path = 


boi_forecast_df = read.csv(paste0(file.path(Sys.getenv("USERPROFILE"),"Documents"),
                                  "\\Data",
                                  "\\BOI\\DSGE",
                                  "\\DSGE and staff forecasts.csv"),
                           stringsAsFactors = FALSE) %>% 
  rename(Date = 1)  %>% 
  mutate(Date = as.Date(Date, format = "%m/%d/%Y")) %>% 
  mutate(Date = as.yearqtr(Date)) %>% 
  filter_at(.vars = vars(-Date),.vars_predicate = any_vars(!is.na(.))) %>% 
  rename_at(.vars = vars(-Date),.funs = list(~gsub("bi.staff_fct_","",.))) %>% 
  rename_at(.vars = vars(-Date),.funs = list(~gsub("_08","",.))) %>%
  rename_at(.vars = vars(-Date),.funs = list(~gsub("\\.Q$","",.))) %>% 
  gather(key = Category, value = BOI_forecast, -Date) %>% 
  separate(Category,into = c("Category","Horizon"),sep = "_",
           extra = "merge") %>% 
  mutate(Horizon = gsub(pattern = "exg_",replacement = "",
                         x = Horizon, fixed = TRUE)) %>% 
  filter(grepl(pattern = "Q",x = Horizon)) %>% 
  mutate(Horizon = gsub(pattern = "Q_",replacement = "",x = Horizon,
                        fixed = TRUE)) %>% 
  mutate(BOI_forecast = BOI_forecast * 0.01)



```


\subsection{Comparison to actual GDP}

We take the predicted YoY GDP growth rates and compare them with actual
GDP YoY growth rates. That basicaly means looking at the residual
(difference between actual and predicted) values of the qunatile regression. The accuracy measures for different time horizons are summarized in table
\ref{forecast_accuracy}


```{r forecast_error}

error_df = list(gar_forecast %>% 
                  filter(Quantile == "0.50",
                         Forecast_Status == "In Sample") %>% 
                  select(Date, Horizon, GaR_forecast) %>% 
                  inner_join(gar_actual_df, by = c("Date","Horizon")) %>% 
                  mutate(Forecast_Error = GaR_actual - GaR_forecast) %>% 
                  select(Date,Horizon,Forecast_Error) %>% 
                  mutate(Indicator = "In sample"),
                gar_forecast %>% 
                  filter(Quantile == "0.50",
                         Forecast_Status == "Out of Sample") %>% 
                  select(Date, Horizon, GaR_forecast) %>% 
                  inner_join(gar_actual_df, by = c("Date","Horizon")) %>% 
                  filter(complete.cases(.)) %>% 
                  mutate(Forecast_Error = GaR_actual - GaR_forecast) %>% 
                  select(Date,Horizon,Forecast_Error) %>%
                  mutate(Indicator = "Out of sample"),
                naive_forecast_df %>% 
                  select(Date, Naive_Next_Q) %>% 
                  inner_join(gar_actual_df %>% 
                               filter(Horizon ==1) %>% 
                               select(Date,Horizon, GaR_actual),
                             by = "Date") %>% 
                  filter(complete.cases(.)) %>% 
                  mutate(Forecast_Error = GaR_actual - Naive_Next_Q) %>% 
                  select(Date,Horizon,Forecast_Error) %>%
                  mutate(Indicator = "Naive_Forecast"),
                boi_forecast_df %>% 
                  filter(Category == "shiputit") %>% 
                  select(Date, Horizon, BOI_forecast) %>% 
                  inner_join(gar_actual_df, by = c("Date","Horizon")) %>% 
                  filter(complete.cases(.)) %>% 
                  mutate(Forecast_Error = GaR_actual - BOI_forecast) %>% 
                  select(Date,Horizon,Forecast_Error) %>%
                  mutate(Indicator = "BoI_forecast")) %>%  
  bind_rows()

error_df = error_df %>% 
  mutate(Horizon = factor(Horizon, levels = c("1","8","12"),
                          labels = c("1","8","12"))) %>% 
  mutate(Indicator = factor(Indicator,
                            levels = c("BoI_forecast","Naive_Forecast",
                                       "In sample","Out of sample"),
                            labels = c("BoI_forecast","Naive_Forecast",
                                       "In sample","Out of sample")))


```


```{r plot_errors}

ggplot(error_df, aes(x = Date, y = Forecast_Error, color = Horizon)) + 
  geom_line() + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  labs(y = "", x = "", title = "Forecast Errors") + 
  scale_x_yearqtr() +
  theme_bw() + 
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5)) + 
  facet_wrap(~Indicator,nrow = 2,ncol = 2)


```


```{r calculate_accuracy_table}

forecast_accuracy_table = error_df %>% 
  group_by(Indicator, Horizon) %>% 
  summarise(RMSE = sqrt(mean(Forecast_Error ^ 2)) * 100,
            MAD = mean(abs(Forecast_Error)) * 100) %>% 
  mutate_if(.predicate = is.numeric,.funs = list(~round(.,3)))



```


```{r output_accuracy_table, results='asis'}

stargazer(forecast_accuracy_table %>% 
            ungroup() %>% 
            mutate(Indicator = as.character(Indicator)) %>% 
            mutate(Horizon = as.character(Horizon)),
          summary = FALSE, header = FALSE,
          label = "forecast_accuracy",
          title = "Forecast accuracy")

```


```{r plot_accuracy_table, eval=FALSE}

ggplot(forecast_accuracy_table, aes(x = Horizon, y = MAD,
                                    fill = Indicator)) + 
  geom_bar(stat = "identity",position = "dodge", width = 0.5) + 
  scale_fill_manual(values = c("red","blue","black","gray")) + 
  theme_bw() + 
  theme(legend.position = "bottom")

```



\subsection{Naive forecast comparison}





<!-- In this section we'll compare the quantile regression predictions to BoI staff forecast. There are two types of comparison:  -->

<!-- \begin{itemize} -->
<!--   \item -->
<!--   Fixed prediction - the prediction is based on a coefficients estimated using -->
<!--   the entire sample (that is simply the fitted values of the qunatile regression). -->
<!--   \item -->
<!--   Rolling prediction - the prediction is based on a coefficients estimated using -->
<!--   the subset sample that is increased at each step. -->

<!-- \end{itemize} -->


```{r merge_data, eval=FALSE}

forecast_df = list(boi_forecast_df,
                   gar_forecast_df %>% 
                     filter(Quantile == 0.5) %>% 
                     select(Date, Horizon, GaR_forecast)) %>% 
  reduce(inner_join, by = c("Date","Horizon")) %>% 
  mutate(GaR_forecast = GaR_forecast * 100) %>% 
  mutate(Diff = GaR_forecast - BOI_forecast)

```


```{r plot, eval=FALSE}

ggplot(forecast_df %>% 
         filter(!is.na(Diff)),
       aes(x = Date, y = Diff, color = Horizon)) + 
  geom_line() + 
  scale_x_yearqtr() + 
  labs(title = "Difference between BOI and GaR forecasts") + 
  theme_bw() + 
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))

```

