---
title: "Growth at Risk model"
institute: "Bank of Israel \\newline Research Department, Finance Division"
author: "Michael Gurkov"
# date: "August 15, 2018"
classoption: t
output:
  beamer_presentation:
    keep_tex: true
    includes:
      in_header: GaR-preamble-presentation.tex
    latex_engine: xelatex
vignette: >
  %\VignetteIndexEntry{GlobalFinCycle-Presentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, echo = FALSE, message = FALSE,warning = FALSE,
  comment = "#>"
)
```


```{r init_setup}

devtools::load_all()

library(GaRPackg)

# setwd(paste0(file.path(Sys.getenv("USERPROFILE"),"Documents",fsep="\\"),
#        "\\GaRPackg\\vignettes"))

# setwd(paste0(file.path(Sys.getenv("USERPROFILE"),"Documents",fsep="/"),
#        "/GaRPackg/vignettes"))


```

# Background

\begin{itemize}
	\item
	Macro-financial model  developed by {adrian2019vulnerable}.
	
	
	\begin{itemize}
		\item Operationalized by IMF {prasad2019growth}.
		\item
		Applied for: 
		\begin{itemize}
			\item[] Italy {\scriptsize{Alessandri2019}}
			\item[] UK {\scriptsize{Aikman2018}}
			\item[] advanced economies {\scriptsize{Aikman2019}}
			\item[] developing economies {\scriptsize{Komatsuzaki2019,Bespalova2019}}
		\end{itemize}
		 
		\item
		First run in Israel (based on IMF modelling): box in  Financial Stability Report 2019(1)
	\end{itemize}
	
	\item
	Today: 
	\begin{itemize}
		\item
		Further adjustments of the model to Israel
		\item
		Discussion of main findings (corresponding to {adrian2019monetary})
		
	\end{itemize}
\end{itemize}	
	



# Motivation

\begin{itemize}
	
	\item
	Goal: Estimate risks to growth using real and financial variables:	
	
	\begin{center}	
		~
	\begin{beamerboxesrounded}[width=0.75\linewidth]{}
		Given current macro-financial conditions, what is the distribution of
		expected economic growth?		
	\end{beamerboxesrounded}
	~
	\end{center}
	

	
	\item
	Tool: Linear  model of
	density forecasts. 
	
	\begin{itemize}
		\item
		Based on quantile regressions
		\item
		Parsimonious
		\item
		Easy to interpret
		
				
	\end{itemize}
	
	\item
	Possible uses:
	\begin{enumerate}
		
		\item
		Tool for regular assessment of risks:
		\begin{itemize}
			\item
			Financial Stability Report
			\item
			Staff forecast fan chart
		\end{itemize}
		
		\item
		Provide empirical evidence to support macro-financial  modelling efforts (joint project with IMF)
		
		
		
	\end{enumerate}
		
\end{itemize}


# Outline

\tableofcontents[sectionstyle=show/show,subsectionstyle=hide/hide] 
