
\subsection{Data}

Our data includes `r ncol(raw_data$raw_df)` variables
(at quarterly frequency) for
`r paste(range(raw_data$raw_df$Date), collapse = "-")` period.

The following transformations were performed:

\begin{enumerate}
  \item
  Dom Real partition variables and CA are transformed with rolling
  (4 quarter window) sum.
  \item
  CA in normalized by GDP
  \item
  Selected variables(real activity, prices, credit, etc) are transformed
  to YoY rates of change.
  \item
  Selected rates variables are transformed to spreads by subtracting the
  benchmark (long term) rate.


\end{enumerate}


\subsection{Data structure}

```{r plot_data_structure, fig.height=8, eval=FALSE}

ggplot(raw_data$raw_df
       %>%
  mutate_at(.vars = vars(-Date),
            .funs = list(~is.na(.))) %>%
  gather(key = Indicator, value = Missing, -Date) %>% 
    mutate(Missing = as.factor(Missing)) %>% 
    group_by(Indicator) %>% 
    mutate(Miss_count = sum(Missing == TRUE)) %>% 
    ungroup(),
  aes(x = Date, y = reorder(Indicator, Miss_count),color = Missing)) + 
  geom_point(size = 0.6) + 
  scale_color_manual(values = c("FALSE" = "lightgray",
                                "TRUE" = "magenta")) +
  scale_x_yearqtr(format = "%YQ%q",n = 25) + 
  labs(x = "",y = "", title = "Missing data structure") + 
  theme_bw() + 
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, vjust = 0.5),
        axis.text.y = element_text(size = 4),
        plot.title = element_text(hjust = 0.5))

```


The following series were dropped because of short length

```{r drop_series_list, results='asis'} 

cat(paste('-', parameters_list$drop_series), sep = '\n') 

``` 


```{r child="GaR-Variables-Desc-Chart.Rmd"}

```

