---
title: "Inflation Risks in Israel"
author: "Michael Gurkov and Osnat Zohar"
institute: "Bank of Israel \\newline Research Department \\newline \\newline Any views expressed in the Discussion Paper are those of the authors and do not necessarily reflect those of the Bank of Israel"
date: "27 July, 2021"
classoption: t
output:
  beamer_presentation:
    includes:
      in_header: !expr here::here('vignettes/GaR-PresentationPreamble.tex')
    latex_engine: xelatex
    slide_level: 2
# bibliography: "GaR.bib"
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, echo = FALSE, message = FALSE,
  warning = FALSE, comment = "#>"

)
```


```{r init_setup}

devtools::load_all()

library(ggcorrplot)

library(mFilter)

library(tidyverse)

library(lubridate)

library(slider)

library(cowplot)

library(broom)

library(gghighlight)

library(glue)

setwd(paste0(
  file.path(Sys.getenv("USERPROFILE"),fsep = "\\"),
  "\\Documents\\GaRPackg\\vignettes"))


```



```{r set_params}

partitions_list = list(
  inflation = c("cpi"),
  exchange_rate = c("nis_usd"),
  oil_p = c("brent_usd"),
  output_gap = c("meshulav_gap"),
  expectation = c("beir5y5y")
)

partitions_list_zlb = c(partitions_list,
                        list(zlb_dummy = "zlb_indicator"))

partitions_list_zlb_complete = c(partitions_list_zlb,
                                 list(cpi_zlb = "cpi_zlb",
                                      nis_usd_zlb = "nis_usd_zlb",
                                      brent_usd_zlb = "brent_usd_zlb",
                                      meshulav_gap_zlb = "meshulav_gap_zlb",
                                      beir5y5y_zlb = "beir5y5y_zlb"))


horizon_list=c(1,12)

quantile_vec=c(0.10,0.25,0.5,0.75,0.90)



theme_set(theme_bw() + 
            theme(title = element_text(size = 20),
                axis.text = element_text(size = 15),
                axis.title = element_text(size = 15),
                strip.text = element_text(size = 15),
                legend.position = "bottom",
                legend.title = element_blank(),
                legend.text = element_text(size = 15)))

# plot_names = tribble(
#   ~var_name, ~plot_name,
#   "Intercept", "Intercept",
#   "cpi", "Inflation",
#   "cpi_lag", "Inflation",
#   "spf1y","Expectations",
#   "beir5y5y","LT Expect.",
#   "nis_usd", "Exchange Rate",
#   "rel_tradables", "Tradables",
#   "brent_usd", "Oil Prices",
#   "meshulav_gap","Output Gap"
# )



```

```{r load_data}

raw_df = import_from_fame_template(
  paste0(
    file.path(Sys.getenv("USERPROFILE")),
    "\\OneDrive - Bank Of Israel\\Data\\BoI\\IaR_data\\data_Inflation_at_Risk_monthly.csv"
  ),data_frequency = "monthly"
)

df = raw_df %>% 
  mutate(rel_tradables = cpi_tradables / cpi_nontradables_excl_fv_hous) %>%
  preprocess_df(
    vars_to_yoy = c(
      "cpi",
      "cpi_excl_fv",
      "cpi_excl_fv_hous",
      "cpi_excl_hous",
      "rel_tradables",
      "cpi_oecd",
      "cpi_us",
      "cpi_euro",
      "debt_business",
      "debt_households",
      "house_price",
      "ta125"
    ),
    vars_to_percent_changes = c("nis_usd",
                                "neer",
                                "brent_usd",
                                "brent_nis",
                                "non_energy_p"),
    convert_to_percent_units = TRUE
  ) %>%
  mutate(target = target * 100) %>% 
  mutate(cpi_orig = cpi) %>% 
  mutate(cpi = cpi_excl_fv_hous) %>% 
  mutate(cpi_lag = lag(cpi)) %>% 
  filter(year(date) >= 2004 & year(date) <= 2019)

filter_obj =  hpfilter(df$madad_meshulav,freq = 1600)

df = df %>% 
  mutate(meshulav_gap = filter_obj$cycle / filter_obj$trend[,1] * 100)

df = df %>% 
  select(date, unlist(partitions_list, use.names = FALSE)) %>% 
  mutate(zlb_indicator = if_else(year(date) >= 2014,1,0)) %>% 
  mutate(across(c("cpi","nis_usd","brent_usd","meshulav_gap","beir5y5y"),
                ~ . * zlb_indicator,.names = "{.col}_zlb"))


```

```{r run_analysis}

iar_analysis = run_GaR_analysis(
  partitions_list = partitions_list_zlb,
  vars_df = df,
  target_var_name = "cpi",
  horizon_list = horizon_list,
  quantile_vec = quantile_vec,
  pca.align.list = list(
    output_gap = list("output_gap", TRUE),
    expectation = list("beir5y5y", TRUE)
  )
)

ols_coeffs = iar_analysis$reg_df %>%
  select(cpi_12, ends_with("xreg")) %>%
  lm(paste("cpi_12 ~ ."), .) %>%
  tidy() %>%
  filter(!term == "(Intercept)") %>%
  mutate(term = str_remove_all(term, "_xreg")) %>%
  mutate(partition = factor(
    term,
    levels = c(
      "cpi",
      "beir5y5y" ,
      "meshulav_gap",
      "brent_usd",
      "nis_usd",
      "zlb_indicator"
    ),
    labels = c(
      "Inflation",
      "Expectations",
      "Output Gap",
      "Oil prices",
      "Exchange Rate",
      "ZLB"
    )
  )) %>%
  select(partition, estimate)


```

```{r iqr_df}

iqr_df = iar_analysis %>% 
  calculate_skew_and_iqr()

```


```{r out_of_sample_forecast}

win_len = 109

iar_forecast = get_gar_forecast(partitions_list = partitions_list,
                                vars_df = df,
                                target_var_name = "cpi",
                                horizon_list = horizon_list,
                                quantile_vec = quantile_vec,
                                win_len = win_len,
                                win_type_expanding = TRUE)

intercept_forecast = get_gar_forecast(partitions_list = NULL,
                                vars_df = df,
                                target_var_name = "cpi",
                                horizon_list = horizon_list,
                                quantile_vec = quantile_vec,
                                win_len = win_len,
                                win_type_expanding = TRUE)

inflation_forecast = get_gar_forecast(partitions_list = list(inflation = "cpi"),
                                vars_df = df,
                                target_var_name = "cpi",
                                horizon_list = horizon_list,
                                quantile_vec = quantile_vec,
                                win_len = win_len,
                                win_type_expanding = TRUE)

rm(win_len)


```





## Positive Inflation and Oil Price Coefficients, Negative Output Gap

\label{coef_results}


```{r plot_coeffs_draft, fig.height=7.5,eval=FALSE}

coeff_df = iar_analysis %>%
  extract_coeffs_from_gar_model() %>%
  filter(!partition == "Intercept") %>%
  filter(horizon == 12) %>% 
  select(-horizon) %>% 
  mutate(partition = factor(
    partition,
    levels = c("cpi","beir5y5y" ,"meshulav_gap","brent_usd","nis_usd",
               "zlb_indicator"),
    labels = c("Inflation","Expectations","Output Gap", "Oil prices",
               "Exchange Rate","ZLB")
  ))


ggplot() +
  geom_col(data = coeff_df, aes(x = quantile, y = coeff, fill = significant),
           width = 0.3) +
  scale_fill_manual(values = c("significant" = "lightblue","non_significant" = "gray"),
                    labels = c("Significant", "Non significant")) +
  facet_grid(rows = vars(partition), scales = "free") +
  geom_hline(data = ols_coeffs,aes(yintercept = estimate,linetype = "OLS"),
             color = "blue") +
  scale_linetype_manual(values = "dashed") + 
  xlab("Quantile") + ylab(NULL) +
  labs(
    caption = paste0(
      "Notes: Each column shows the estimated coefficients ",
      "from the quantile regression at a specific forecast horizon. ",
      "\n  Blue bars mark coefficients that are significant at 10%",
      "(see Koenker, 1994)"
    )
  ) +
  theme(plot.caption = element_text(size = 10, hjust = 0.5),
        axis.text.x = element_text(size = 12),
        strip.text = element_text(size = 12))

```


```{r plot_coeffs,fig.width=13, fig.height=8}

coeff_df = iar_analysis %>%
  extract_coeffs_from_gar_model() %>%
  filter(!partition == "Intercept") %>%
  filter(horizon == 12) %>% 
  select(-horizon) %>% 
  mutate(partition = factor(
    partition,
    levels = c("cpi","beir5y5y" ,"meshulav_gap","brent_usd","nis_usd",
               "zlb_indicator"),
    labels = c("Inflation","Expectations","Output Gap", "Oil prices",
               "Exchange Rate","ZLB")
  ))


ggplot() +
  geom_col(data = coeff_df, aes(x = quantile, y = coeff, fill = significant),
           width = 0.3) +
  scale_fill_manual(values = c("significant" = "lightblue","non_significant" = "gray"),
                    labels = c("Significant", "Non significant")) +
  facet_wrap(~partition, scales = "free") +
  geom_hline(data = ols_coeffs,aes(yintercept = estimate,linetype = "OLS"),
             color = "blue") +
  scale_linetype_manual(values = "dashed") + 
  geom_hline(yintercept = 0, color = "black") + 
  xlab("Quantile") + ylab(NULL) +
  labs(
    caption = paste0(
      "Notes: Each column shows the estimated coefficients ",
      "from the quantile regression. ",
      "\n  Blue bars mark coefficients that are significant at 10%",
      "(see Koenker, 1994)"
    )
  ) +
  theme(plot.caption = element_text(size = 10, hjust = 0.5),
        axis.text.x = element_text(size = 12),
        strip.text = element_text(size = 12))

```

\hyperlink{OutACf}{\beamerbutton{Output gap ACF}}



# In-sample Features of the Forecast Distribution
## Downside Risks Increase After 2014

```{r plot_dist_timeseries}

plot_df = iar_analysis$fitted_df %>%
  filter(quantile %in% c(0.25,0.5,0.75)) %>%
  filter(horizon == 12) %>%
  select(-horizon) %>%
  group_by(date = as.yearqtr(date), quantile) %>%
  summarise(avg_values = mean(fitted_values) * 4, .groups = "drop")

ggplot() +
  geom_line(data = plot_df %>%
              filter(quantile == "0.5"), aes(x = date, y = avg_values)) +
  geom_ribbon(data = plot_df %>%
                filter(quantile %in% c(0.25,0.75)) %>%
                pivot_wider(names_from = "quantile",
                            names_prefix = "q_",
                            values_from = "avg_values"),
              aes(x = date, ymin = q_0.25, ymax = q_0.75), alpha = 0.5) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1,scale = 1)) +
  ylab(NULL) + xlab(NULL)  +
  ggtitle("Predicted annual inflation one year ahead (quarterly averages)")


```


## Lower Dispersion and Higher Downside Risks after 2014

```{r plot_skewness_1_quarter, fig.height=6}

n = nrow(df)

skew_se=sqrt( 6*n*(n-1) / ((n-2)*(n+1)*(n+3)) )

skew_df = iqr_df %>%
  filter(horizon == 12) %>% 
  select(-horizon) %>%
  pivot_longer(-date) %>%
  # group_by(date = as.yearqtr(date), name) %>%
  # summarise(value = mean(value), .groups = "drop") %>%
  mutate(name = factor(name, levels = c("iqr","skew"),
                       labels = c("Dispersion","Skewness")))

hline_df = skew_df %>%
  group_by(name) %>%
  summarise(val = mean(value)) %>% 
  mutate(color = "blue") %>% 
  mutate(linetype = "solid") %>% 
  bind_rows(tibble(name = rep("Skewness",2),
                   val = c(2 * skew_se, -2 * skew_se),
                   color = "black",
                   linetype = "dashed")) %>% 
  bind_rows(tibble(name = "Skewness",
                   val = 0,
                   color = "black",
                   linetype = "solid"))

skew_df%>%
  ggplot(aes(x = date, y = value)) +
  geom_line() +
  facet_wrap(~name, scales = "free") +
  geom_hline(aes(yintercept = val, color = color, linetype = linetype),
             data = hline_df, show.legend = FALSE) + 
  scale_color_manual(values = c("black" = "black","blue" = "blue")) + 
  scale_linetype_manual(values = c("solid" = "solid", "dashed" = "dashed")) + 
  labs(x = "", y = "",
       caption = "Note: the dashed lines represent ± 2 standard error estimates") +
  theme(plot.caption = element_text(hjust = 0.5))


 rm(skew_df, hline_df, skew_se, n)

```

$Dispersion_{t} \equiv Q^{75}_{t} - Q^{25}_{t} \quad Skeweness_{t} \equiv \frac{Q^{75}_{t} + Q^{25}_{t} -2Q^{50}_{t}}{Dispersion_{t}}$

## Inflation environment and oil prices are the dominant risk factors

\label{FactorPlot}


```{r factor_decomposition_deviations}

means_vec = iqr_df %>% 
  filter(horizon == 12) %>% 
  select(skew,iqr) %>% 
  summarise(across(everything(), mean))


median_mean = iar_analysis$fitted_df %>% 
  filter(quantile == "0.5") %>% 
  pull(fitted_values) %>% 
  mean()

labels_df = tibble(
  level = c("cpi", "nis_usd", "brent_usd", "meshulav_gap", "exp_int",
            "zlb_indicator"),
  label = c(
    "Inflation",
    "Exchange Rate",
    "Oil prices",
    "Output Gap",
    "Exp. and Intercept",
    "ZLB"
  )
)

factors_cont_df = iar_analysis %>%
  extract_factor_contribution_from_gar_model(target_quantile = "0.25") %>%
  mutate(quantile = 0.25) %>%
  bind_rows(iar_analysis %>%
  extract_factor_contribution_from_gar_model(target_quantile = "0.75") %>%
  mutate(quantile = 0.75)) %>%
  bind_rows(iar_analysis %>%
  extract_factor_contribution_from_gar_model(target_quantile = "0.5") %>%
  mutate(quantile = 0.5)) %>%
  filter(horizon == 12) %>% 
  filter(date >= as.yearmon("Jan 2007")) %>% 
  pivot_longer(-c(date, quantile, horizon))


skew_plot_df = factors_cont_df %>% 
  pivot_wider(id_cols = c(date,name, horizon), names_from = quantile,
              names_prefix = "q_") %>% 
  left_join(iqr_df, by = c("date", "horizon")) %>% 
  mutate(skew_cont = (q_0.75 + q_0.25 - 2 * q_0.5) / iqr) %>% 
  select(-starts_with("q_"),-horizon,-iqr) %>% 
  group_by(date = as.yearqtr(date), name) %>% 
  summarise(across(everything(),mean, na.rm = TRUE), .groups = "drop")  %>% 
  pivot_wider(names_from = name, values_from = skew_cont) %>% 
  mutate(exp_int = intercept + beir5y5y - means_vec$skew) %>% 
  mutate(skew = skew - means_vec$skew) %>%
  select(-c(intercept,beir5y5y)) %>% 
  pivot_longer(-c(date,skew)) %>% 
  mutate(name = factor(name,levels = labels_df$level, labels = labels_df$label))


disp_plot_df = factors_cont_df %>% 
  pivot_wider(id_cols = c(date,name, horizon), names_from = quantile,
              names_prefix = "q_") %>% 
  left_join(iqr_df, by = c("date", "horizon")) %>% 
  mutate(iqr_cont = q_0.75 - q_0.25) %>%
  select(-starts_with("q_"),-horizon,-skew) %>% 
  group_by(date = as.yearqtr(date), name) %>% 
  summarise(across(everything(),mean, na.rm = TRUE), .groups = "drop")  %>% 
  pivot_wider(names_from = name, values_from = iqr_cont) %>% 
  mutate(exp_int = intercept + beir5y5y - means_vec$iqr) %>% 
  mutate(iqr = iqr - means_vec$iqr) %>% 
  select(-c("intercept","beir5y5y")) %>% 
  pivot_longer(-c(date,iqr)) %>% 
  mutate(name = factor(name,levels = labels_df$level, labels = labels_df$label))



median_plot_df = factors_cont_df %>% 
  pivot_wider(id_cols = c(date,name, horizon), names_from = quantile,
              names_prefix = "q_") %>% 
  mutate(med_cont = q_0.5) %>%
  select(-starts_with("q_"),-horizon) %>% 
  group_by(date = as.yearqtr(date), name) %>% 
  summarise(across(everything(),mean, na.rm = TRUE), .groups = "drop")  %>% 
  pivot_wider(names_from = name, values_from = med_cont) %>% 
  mutate(exp_int = intercept + beir5y5y - median_mean) %>% 
  select(-c("intercept","beir5y5y")) %>% 
  pivot_longer(-c(date)) %>% 
  mutate(name = factor(name,levels = labels_df$level, labels = labels_df$label))



```


```{r plot_factor_decomposition, fig.height=7.5}

skew_plot = ggplot() + 
  geom_col(aes(x = date, y = value, fill = name), data = skew_plot_df) + 
  geom_line(aes(x = date, y = skew), data = skew_plot_df, size = 1) + 
  xlab(NULL) + ylab(NULL) + ggtitle("Skewness")


disp_plot =  ggplot() + 
  geom_col(aes(x = date, y = value, fill = name), data = disp_plot_df) + 
  geom_line(aes(x = date, y = iqr), data = disp_plot_df, size = 1) + 
  xlab(NULL) + ylab(NULL) + ggtitle("Dispersion")

med_plot =  ggplot() + 
  geom_col(aes(x = date, y = value, fill = name), data = median_plot_df) + 
  geom_line(aes(x = date, y = value), data = median_plot_df %>% 
              group_by(date) %>% 
              summarise(value = sum(value), .groups = "drop"), size = 1) +
  xlab(NULL) + ylab(NULL) + ggtitle("Median") + 
  labs(caption = "Deviations from the mean")


plot_legend = get_legend(disp_plot)

plots_row = plot_grid(disp_plot +
            theme(legend.position = "none"),
          skew_plot +
            theme(legend.position = "none"),
          med_plot +
            theme(legend.position = "none",
                  plot.caption = element_text(hjust = 0)))

plot_grid(plots_row, plot_legend,nrow = 2,rel_heights = c(4,1))



```


\vspace{-2em}


\begin{flushright}
\hyperlink{OutGap}{\beamerbutton{Output gap}}
\end{flushright}

<!-- \scriptsize -->

<!-- $E(Disp_{t + 12}|X_{t}) = (\beta^{75} - \beta^{25})X_{t} \quad E(Skew_{t + 12}|X_{t}) = \frac{(\beta^{75}_{t}+\beta^{25}_{t}-2\beta^{50}_{t})X_{t}}{Disp_{t+12}}$ -->


## Realized inflation increases upside risks and uncertainty one year ahead


```{r inflation_iqr}

iqr_df %>%
  filter(horizon == 12) %>%
  left_join(select(df, c(date, cpi)), by = "date") %>%
  left_join(iar_analysis$fitted_df %>%
              filter(quantile == 0.5) %>%
              select(date, horizon, median = fitted_values)) %>%
  pivot_longer(cols = c(skew,iqr,median)) %>%
  mutate(name = factor(name, levels = c("median", "iqr","skew"),
                       labels = c("Median","Dispersion","Skewness"))) %>%
  ggplot(aes(x = cpi, y = value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~name, scales = "free") +
  scale_x_continuous(labels = scales::percent_format(scale = 1, accuracy = 1)) +
  xlab("Realized inflation") + ylab(NULL)

```


## Inflation expectations increase upside risks and lowers uncertainty one year ahead


```{r expectation_iqr}

iqr_df %>%
  filter(horizon == 12) %>%
  left_join(select(df, c(date, beir5y5y)), by = "date") %>%
  left_join(iar_analysis$fitted_df %>%
              filter(quantile == 0.5) %>%
              select(date, horizon, median = fitted_values)) %>%
  pivot_longer(cols = c(skew,iqr,median)) %>%
  mutate(name = factor(name, levels = c("median", "iqr","skew"),
                       labels = c("Median","Dispersion","Skewness"))) %>%
  ggplot(aes(x = beir5y5y, y = value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~name, scales = "free") +
  scale_x_continuous(labels = scales::percent_format(scale = 1, accuracy = 0.1)) +
  xlab("Inflation expectations") + ylab(NULL) + 
  theme(axis.text.x = element_text(hjust = 0.25))

```


## Oil prices stimulate inflation and decreases uncertainty and skeweness one year ahead


```{r oil_gap_iqr}

iqr_df %>%
  filter(horizon == 12) %>%
  left_join(select(df, c(date, x = brent_usd))) %>%
  left_join(iar_analysis$fitted_df %>%
              filter(quantile == 0.5) %>%
              select(date, horizon, median = fitted_values)) %>%
  pivot_longer(cols = c(skew,iqr,median)) %>%
  mutate(name = factor(name, levels = c("median", "iqr","skew"),
                       labels = c("Median","Dispersion","Skewness"))) %>%
  ggplot(aes(x = x, y = value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~name, scales = "free") +
  scale_x_continuous(labels = scales::percent_format(scale = 1)) +
  xlab("Oil price") + ylab(NULL)

```


# Out-of-Sample Forecast Performance
## Out-of-Sample Forecast

```{r out_of_sample_forecast_plot}

ggplot() +
  geom_ribbon(
    data = iar_forecast %>%
      filter(horizon == 12) %>%
      filter(quantile %in% c("0.10", "0.90")) %>%
      mutate(date = date + as.numeric(horizon)  / 12) %>%
      pivot_wider(
        names_from = "quantile",
        names_prefix = "q_",
        values_from = "forecast_values"
      ),
    aes(
      x = date,
      ymin = q_0.10,
      ymax = q_0.90,
      fill = "80% of Distribution"
    ),
    alpha = 0.5) +
    geom_ribbon(
    data = iar_forecast %>%
      filter(quantile %in% c(0.25, 0.75)) %>%
      filter(horizon == 12) %>%
      mutate(date = date + as.numeric(horizon)  / 12) %>%
      pivot_wider(
        names_from = "quantile",
        names_prefix = "q_",
        values_from = "forecast_values"
      ),
    aes(
      x = date,
      ymin = q_0.25,
      ymax = q_0.75,
      fill = "50% of Distribution"
    ),
    alpha = 0.8) +
    geom_line(
    data = iar_forecast %>%
      filter(quantile == "0.50") %>%
      filter(horizon == 12) %>%
      mutate(date = date + as.numeric(horizon)  / 12),
    aes(x = date, y = forecast_values, color = "Forecasted Median 12 Month Earlier")
  ) +
  geom_line(
    data = df %>%
      filter(
        date >= iar_forecast %>%
          filter(horizon == 12) %>%
          pull(date) %>% min() + 1
      ),
    aes(x = date, y = cpi, color = "Realized Inflation")
  ) + 
  ylab("Percent") + xlab(NULL) +
  ggtitle("Quantiles of inflation") + 
  scale_fill_manual(values = c("grey","lightblue")) + 
  scale_color_manual(values = c("black","red")) + 
  theme(legend.text = element_text(size = 12))



```


## Out-of-Sample Forecast Performance

\vspace{2em}

\begin{itemize}
\setlength\itemsep{2em}
	\item
	IaR model compared to two alternatives:
	\begin{enumerate}
		\item
		Intercept only -- partial IaR model without explanatory variables
		\item
		Intercept and realized inflation -- partial IaR model
	\end{enumerate}
	\item
	The models are evaluated out of sample (expanding window starts at
	85 observations and adds one observation in each step)
\end{itemize}

## Probability Integral Transform (PIT)

\label{PIT}


For each quantile $\tau$ we compute  the percentage of observations that fall below the forecast quantile $\hat{Q}^{\tau}_{t}$:
	$$
	\varphi_{\tau} \equiv \frac{1}{T} \sum_{t=1}^{T} \mathbb{I}_{ \left\{ y_{t} <  \hat{Q}^{\tau}_{t} \right\} }.
	$$
\begin{itemize}
\setlength\itemsep{1em}
	\item
	A model is better fitted the closer $\varphi_{\tau}$ is to
	45-degree line.
	\item
	If the model perfectly fits the empirical  distribution, then
	the fraction of observations falling below quantile $\tau$
	should be exactly $\tau$, namely, $\varphi_{\tau}=\tau$.
\end{itemize}


\hyperlink{PITscore}{\beamergotobutton{PITscore}}

## Goodness of fit -- PIT score \newline (the closer to the black line the better)

\label{PITscore}

```{r pit_score}

iar_pit = quantile_pit_score(
  forecast_df = iar_forecast %>%
    filter(horizon == 12),
  actual_df = select(df, actual_values = cpi, date)) %>%
  rename(iar = pit)

intercept_pit = quantile_pit_score(
  forecast_df = intercept_forecast  %>%
    filter(horizon == 12),
  actual_df = select(df, actual_values = cpi, date)) %>%
  rename(intercept = pit)

inflation_pit = quantile_pit_score(
  forecast_df = inflation_forecast %>%
    filter(horizon == 12),
  actual_df = select(df, actual_values = cpi, date)) %>%
  rename(realized_inflation = pit)

list(iar_pit, intercept_pit, inflation_pit) %>%
  reduce(inner_join, by = c("quantile", "horizon")) %>%
  pivot_longer(-c("quantile", "horizon")) %>%
  mutate(quantile = as.numeric(quantile)) %>%
  mutate(name = factor(name,
                       levels = c("realized_inflation","iar","intercept"),
                       labels = c("CPI only","Inflation at risk","Intercept"))) %>%
  ggplot(aes(x = quantile,y = value,color = name,group = name)) +
  geom_line() +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = "black",
    linetype = "dashed"
  ) +
  xlim(0,1) + ylim(0,1) +
  xlab("Quantile") + ylab(NULL)



```


\hyperlink{PIT}{\beamergotobutton{PIT}}

# Summary

\begin{itemize}
\setlength\itemsep{3em}
  \item
  The decline in inflation since 2014 was associated with a decline in uncertainty
  and a relative rise in downside risks to inflation.
  \item
  The decline in long-term expectations and oil prices played a prominent role
  in these developments.
  \item
  The model can also be used to assess inflation risks regularly. 
  
\end{itemize}

# Appendix {.unlisted .unnumbered}
## Output gap depresses inflation while increasing upside risks one year ahead


```{r output_gap_iqr}

iqr_df %>%
  filter(horizon == 12) %>%
  left_join(select(df, c(date, x = meshulav_gap)), by = "date") %>%
  left_join(iar_analysis$fitted_df %>%
              filter(quantile == 0.5) %>%
              select(date, horizon, median = fitted_values)) %>%
  pivot_longer(cols = c(skew,iqr,median)) %>%
  mutate(name = factor(name, levels = c("median", "iqr","skew"),
                       labels = c("Median","Dispersion","Skewness"))) %>%
  ggplot(aes(x = x, y = value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~name, scales = "free") +
  xlab("Output gap") + ylab(NULL)

```


## Exchange rate increases downside risks and lowers uncertainty one year ahead


```{r fx_rate_iqr}

iqr_df %>%
  filter(horizon == 12) %>%
  left_join(select(df, c(date, x = nis_usd))) %>%
  left_join(iar_analysis$fitted_df %>%
              filter(quantile == 0.5) %>%
              select(date, horizon, median = fitted_values)) %>%
  pivot_longer(cols = c(skew,iqr,median)) %>%
  mutate(name = factor(name, levels = c("median", "iqr","skew"),
                       labels = c("Median","Dispersion","Skewness"))) %>%
  ggplot(aes(x = x, y = value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~name, scales = "free") +
  scale_x_continuous(labels = scales::percent_format(scale = 1,accuracy = 1)) +
  xlab("Exchange rate") + ylab(NULL) + 
  theme(axis.text.x = element_text(hjust = 0.25))
```




## Quantile Regression

\label{QuantileReg}

Model: for quantile $\tau$ and horizon $h$,
$$
Q^{\tau}_{t,h}=\beta^{\tau}_hX_t+\epsilon^{\tau}_{h,t}
$$

$\beta^{\tau}$ is  estimated by solving the minimization problem

$$
\min_{\beta^{\tau}}
\sum_{t=1}^T
\max \bigg\{
\tau \big( y_{t+h}- \beta^{\tau}X_t \big)
\, ,\,
(\tau-1) \big( y_{t+h}- \beta^{\tau}X_t \big)
\bigg\}
$$

Note: "Quantile crossing" handled using the method of Chernozhukov et al. (2010).

\begin{flushleft}
\hyperlink{methodology}{\beamergotobutton{Methodology}}
\end{flushleft}




## Autoregression in Output Gap

\label{OutACf}

```{r output_gap_ar}


out_gap_ar = df %>%
  pull(meshulav_gap) %>%
  acf(plot = FALSE)

tibble(acf = out_gap_ar$acf[,,1], lag = out_gap_ar$lag[,,1]) %>%
  ggplot(aes(x = lag, y = acf, fill = (lag == 12))) +
  geom_col(width = 0.5) +
  geom_hline(yintercept = c(-0.5,0.5), linetype = "dashed") +
  scale_fill_manual(values = c("grey","lightblue")) +
  theme(legend.position = "none") +
  xlab("Lag") + ylab(NULL) + ggtitle("Autocorrelation function of Output Gap")

```


\hyperlink{coef_results}{\beamerbutton{coeffs}}


## Output Gap

\label{OutGap}

```{r output_gap}

df %>% 
  ggplot(aes(x = date, y = meshulav_gap)) + 
  geom_line() + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  xlab(NULL) + ylab(NULL) + ggtitle("Output gap")

```

\hyperlink{FactorPlot}{\beamerbutton{Factor decomposition}}

## Goodness of fit --Quantile R-Squared \newline (the higher the better, negative means worse than intercept only)

```{r plot_r2_score}

iar_r2 = quantile_r2_score(
  forecast_df = iar_forecast,
  actual_df = select(df, actual_values = cpi, date),
  benchmark_df = intercept_forecast %>%
    rename(benchmark_values = forecast_values)) %>%
  rename(iar_r2 = quantile_r2)

inflation_r2 = quantile_r2_score(
  forecast_df = inflation_forecast,
  actual_df = select(df, actual_values = cpi, date),
  benchmark_df = intercept_forecast %>%
    rename(benchmark_values = forecast_values)) %>%
  rename(inflation = quantile_r2)

iar_r2 %>%
  inner_join(inflation_r2,by = c("horizon", "quantile")) %>%
  pivot_longer(-c(horizon, quantile)) %>%
  mutate(quantile = factor(quantile, levels = quantile_vec)) %>%
  ggplot(aes(x = quantile, y = value, fill = name)) +
  geom_col(position = "dodge") +
  scale_fill_discrete(labels = c("IaR","Inflation only")) +
  xlab("Quantile") + ylab(NULL) + 
  facet_wrap(~horizon, scales = "free")

```
